### 2024-03-18 sections/4gluing_alt.tex
Improvements to one version of gluing proof.

\begin{proof}[Proof of \Cref{cor:gluing_falgs}]
    We will first focus on the case of factorization algebras and prove the statement of \Cref{cor:gluing_falgs}. Moreover, because of \Cref{cor:disk_alg=falg}, this means that we will focus on $
    disk[r]_{/M}$-algebras.

@@

    Specifically, by compatibility here we mean that there is a commutative diagram
    %
    \begin{equation}\label{cd:equivs_from_lc}
        \begin{tikzcd}
            \int_{U_-} A_- \arrow[d, "\simeq"] & \int_{U_0 \times \mathbb{R}} A_0 \arrow[d, "\simeq"] \arrow[l] \arrow[r] & \int_{U_+} A_+ \arrow[d, "\simeq"] \\
            \int_{V_-} A_- & \int_{V_0 \times \mathbb{R}} A_0 \arrow[l] \arrow[r] & \int_{V_+} A_+,
        \end{tikzcd}
    \end{equation}
    %
    where the horizontal arrows are induced by the relevant embeddings. A sufficient condition to guarantee compatibility is that all collar-gluings are defined as collar-gluings of $M$ and then inherited to every open submanifold through its embedding in $M$. Focusing on the final two consecutive collar-gluings we get a commutative diagram, which we schematically denote
    %
    \begin{equation}
        \begin{tikzcd}
            -+ & 0+ \arrow[l] \arrow[r] & ++\\
            -0 \arrow[u] \arrow[d] & 00 \arrow[u] \arrow[l] \arrow[r] \arrow[d] & +0 \arrow[d] \arrow[u] \\
            -- & 0- \arrow[l] \arrow[r] & +-,
        \end{tikzcd}
    \end{equation}
    %
    one for each of $U$ and $V$. Stacking these two with the equivalence as connecting arrows is again a commutative diagram. This is enough information to guarantee that after acting with the bar construction in one direction we again get compatible equivalences. The key point being that we consider the collar-gluings on all pieces in both orders to get all the necessary arrows.
\end{proof}

>>>>

\begin{proof}[Proof of \Cref{cor:gluing_falgs}]
    We will first focus on the case of factorization algebras and prove the statement of \Cref{cor:gluing_falgs}. Moreover, because of \Cref{cor:disk_alg=falg}, this means that we will focus on $\disk[r]_{/M}$-algebras.

@@

    Specifically, by compatibility here we mean that there is a commutative diagram
    %
    \begin{equation}\label{cd:equivs_from_lc}
        \begin{tikzcd}
            \int_{U_-} A_- \arrow[d, "\simeq"] & \int_{U_0 \times \mathbb{R}} A_0 \arrow[d, "\simeq"] \arrow[l] \arrow[r] & \int_{U_+} A_+ \arrow[d, "\simeq"] \\
            \int_{V_-} A_- & \int_{V_0 \times \mathbb{R}} A_0 \arrow[l] \arrow[r] & \int_{V_+} A_+,
        \end{tikzcd}
    \end{equation}
    %
    where the horizontal arrows are induced by the relevant embeddings. A sufficient condition to guarantee compatibility is that all collar-gluings are defined as collar-gluings of $M$ and then inherited to every open submanifold through its embedding in $M$. Focusing on the final two consecutive collar-gluings we get a commutative diagram, which we schematically denote
    %
    \begin{equation}
        \begin{tikzcd}
            -+ & 0+ \arrow[l] \arrow[r] & ++\\
            -0 \arrow[u] \arrow[d] & 00 \arrow[u] \arrow[l] \arrow[r] \arrow[d] & +0 \arrow[d] \arrow[u] \\
            -- & 0- \arrow[l] \arrow[r] & +-,
        \end{tikzcd}
    \end{equation}
    %
    one for each of $U$ and $V$. Stacking these two with the equivalence as connecting arrows is again a commutative diagram. This is enough information to guarantee that after acting with the bar construction in one direction we again get compatible equivalences. The key point being that we consider the collar-gluings on all pieces in both orders to get all the necessary arrows.

    \begin{multicols}{2}
        \begin{figure}[H]
            \centering
            \includegraphics[width=5cm]{../images/extend_gluing.png}
            \caption{Extending a collar-gluing.}
            \label{fig:extend_gluing}
        \end{figure}
        %
        The final point to check is that we have not limited ourselves by insisting to only consider collar-gluings which are inherited from ones on $M$. This is best shown in \Cref{fig:extend_gluing}. Namely, given the disk $V \xhookrightarrow{} M$, we can take a larger disk $V'$, which is guaranteed to exist from the fact that $M$ is a manifold. The figure then shows that given any collar-gluing of $V$ we can find one particular collar-gluing of $M$ that extends the one of $V$. Since $V'$ is a disk, the figure does not obscure any detail.
    \end{multicols}
\end{proof}
